%-----------EXPERIENCE-----------------
\section{Research and Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tencent America}{Palo Alto, CA}
      {Senior Research Scientist}{Apr. 2018 -- Present}
      \resumeItemListStart
        \resumeItem{Human Motion Analysis}
          {Launched AI-powered Parkinson’s Disease (PD) diagnosis clinical trial in UK with King’s College London, widely reported by the \href{https://www.bbc.com/news/technology-50675702}{BBC}, the \href{https://www.forbes.com/sites/samshead/2018/10/08/tencent-aims-to-train-ai-to-spot-parkinsons-in-3-minutes/\#5e47e8ed6f36}{Forbes},
          \href{https://www.bloomberg.com/news/articles/2018-10-08/tencent-reaches-into-london-s-tech-hub-for-parkinson-s-partner}{Bloomberg}, and
          the \href{https://www.ft.com/content/183c412a-6766-11e9-9adc-98bf1d35a056}{Finical Times}.}
          
        \resumeItem{2D/3D Hand Pose Estimation}
          {Developed an adversarial network to generate realistic training RGB and depth images for 2D/3D hand pose estimation; Related research published by BMVC'19 and WACV'20.}
        
        \resumeItem{Human Posture Estimation}
        {Developed a video-based postural tremor detection and analysis system.}
      \resumeItemListEnd

      \resumeSubheading
      {Robert Bosch LLC}{Sunnyvale, CA}
      {Postdoctoral Researcher}{Apr. 2017 -- Mar. 2018}
      \resumeItemListStart
        \resumeItem{Reliable Training Data Generation}
          {Developed a sequence-to-sequence deep generative model which can generate reliable augmented training data to learn a robust deep model for action recognition. Related research published by BMVC'18}
        \resumeItem{Human Action/Gesture Recognition}
          {Developed a residual bidirectional recurrent neural network (Residual-BLSTM) for human action recognition.}
        \resumeItem{Gesture Detection}{Developed a bidirectional-GRUs for detecting gesture from untrimmed MoCap streams} 
      \resumeItemListEnd
    
    \resumeSubheading
      {Academia Sinica}{Taipei, Taiwan}
      {Research Assistant}{Jan. 2014 – Jan. 2016}
      \resumeItemListStart
        \resumeItem{Human Action Recognition}
          {Developed an approach based on Conditional Random Fields (CRFs) for recognizing partially observed human actions. Related research published by ACM TOMM, ICASSP'17}
        \resumeItem{Gesture-Based User Interface}
          {Developed a gesture-based imaginary interface for TV remote control. Related research published by ACM MM'13, and a US patent.}
      \resumeItemListEnd
      
      \resumeSubheading
      {National Institute of Informatics (NII)}{Tokyo, Japan}
      {Research Intern}{Aug 2013 – Dec. 2013}
      \resumeItemListStart
        \resumeItem{Human Action Recognition}
          {Investigated machine learning algorithms for human intention discovery}
      \resumeItemListEnd

  \resumeSubHeadingListEnd