
%-----------Publications-----------------
\section{Publication}
% ----------- Papers -------------- %
\textbf{Selected Papers:} \vspace{-3pt}
\PubItemStart
    \pubitem L. Chen, \mikelin, Y. Xie, Y.-Y. Lin, W. Fan, X. Xie, \textbf{DGGAN: Depth-image Guided Generative Adversarial Networks for jointly Disentangling RGB and Depth Images and Estimating 3D Hand Pose}, IEEE Winter Conference on Applications of Computer Vision (WACV), 2020 ~\href{http://openaccess.thecvf.com/content_WACV_2020/papers/Chen_DGGAN_Depth-image_Guided_Generative_Adversarial_Networks_forDisentangling_RGB_and_Depth_WACV_2020_paper.pdf}{\faFileTextO}
    \pubitem L. Chen, \mikelin, Y. Xie, H. Tang, Y. Xue, X. Xie, Y.-Y. Lin, W. Fan, \textbf{TAGAN: Tonality Aligned Generative Adversarial Networks for Realistic Hand Pose Synthesis}, British Machine Vision Conference (BMVC), 2019~\href{http://cvlab.citi.sinica.edu.tw/images/paper/bmvc-chen19-1.pdf}{\faFileTextO}
    \pubitem \mikelin, Y.-Y. Lin, \textbf{Augmenting Motion Capture Data with Neural Data Translation for Human Action Recognition}, British Machine Vision Conference (BMVC), 2018~\href{https://www.citi.sinica.edu.tw/papers/yylin/6363-F.pdf}{\faFileTextO}~\href{https://sites.google.com/view/action-recognition-ndt/}{\faFilm}
    \pubitem \mikelin, Y.-Y. Lin, C.-S. Chen, Y.-P. Hung, \textbf{Learning Conditional Random Fields with Augmented Observations for Partially Observed Action Recognition}, ArXiv:1811.09986~\href{https://arxiv.org/abs/1811.09986}{\faFileTextO}~\href{https://www.youtube.com/watch?v=E-vBxpUF1dU&feature=youtu.be}{\faFilm}
    \pubitem \mikelin, Y.-Y. Lin, C.-S. Chen, Y.-P. Hung, \textbf{Recognizing Partially Observed Human Actions by Observation Filtering and Completion}, ACM Trans. Multimedia Computing, Communications, and Applications (TOMM), Vol. 13 No. 3, pp. 28:1 - 28:23, 2017~\textbf{(Impact Factor: 2.25)}~\href{https://www.citi.sinica.edu.tw/papers/yylin/5891-F.pdf}{\faFileTextO}~\href{https://www.csie.ntu.edu.tw/~d00944001/videos/TOMM_introduction.mp4}{\faFilm}~\href{https://github.com/mikeshihyaolin/citi_dataset/}{\faFileCodeO}~\href{https://sites.google.com/view/citi3ddataset/}{\faDatabase}
    \pubitem \mikelin, Y.-Y. Lin, C.-S. Chen, Y.-P. Hung, \textbf{Learning and Inferring Human Actions with Temporal Pyramid Features based on Conditional Random Fields}, IEEE Int' Conf. Acoustics, Speech and Signal Processing (ICASSP), 2017~\href{http://cvlab.citi.sinica.edu.tw/images/paper/icassp-Lin17.pdf}{\faFileTextO}~\href{https://www.youtube.com/watch?v=dyNFTpIP3Tw&feature=youtu.be}{\faFilm}
    \pubitem \mikelin, C.-K. Shie, S.-C. Chen, Y.-P. Hung, \textbf{AirTouch Panel: A Re-anchorable Virtual Touch Panel}, ACM Conf. Multimedia (ACM MM), 2013~\href{https://www.csie.ntu.edu.tw/~d00944001/videos/AirTouch\%20Panel.mp4}{\faFilm}
    \pubitem \mikelin, C.-K. Shie, S.-C. Chen, Y.-P. Hung, \textbf{Action Recognition for Human-Marionette Interaction}, ACM Conf. Multimedia (ACM MM), 2012 {\textbf {\color{red}(Best Student Paper Award)}}
    \pubitem \mikelin, C.-K. Shie, S.-C. Chen, M.-S. Lee, Y.-P. Hung, \textbf{Human Action Recognition Using Action Trait Code}, Int' Conf. Pattern Recognition (ICPR), 2012.
    \pubitem \mikelin, Y.-C. Lai, L.-W. Chan, and Y.-P. Hung,~\textbf{Real-time 3D Model based Gesture Tracking for Multimedia Control}, Int' Conf. Pattern Recognition (ICPR), 2010
    \pubitem I-C. Chang, \mikelin, \textbf{3D Human Motion Tracking based on Progressive Particle Filter}, Pattern Recognition (PR), Vol. 43, Issue 10, PP. 3621-3635, 2010. \textbf{(Impact Factor: 3.7)}~\href{https://www.csie.ntu.edu.tw/~d00944001/videos/Lin_PR_2010.pdf}{\faFileTextO}~\href{https://www.csie.ntu.edu.tw/~d00944001/videos/Pattern\%20Recognition-\%203D\%20human\%20motion\%20tracking\%20based\%20on\%20a\%20progressive\%20particle\%20filter\%20(Shih-Yao\%20Lin).mp4}{\faFilm}
    \pubitem \mikelin, I-C. Chang, \textbf{Dynamic Kernel Based Progressive Particle Filter for 3D Human Motion Tracking},  Asian Conf. Computer Vision (ACCV), 2009. \textbf{(LNCS)}
    \pubitem \mikelin, I-C. Chang, \textbf{3D Human Motion Tracking Using Progressive Particle Filter}, Int' Symp. Visual Computing (ISVC), 2008. \textbf{(LNCS)}
\PubItemEnd

% ----------- Patents -------------- %
\textbf{Patents:} \vspace{-3pt}
\PubItemStart
    \pubitem \mikelin, Y. Xie, H. Tang, C. Huang, L. Han, W. Fan, \textbf{Video-based 3D Hand Pose and Mesh Estimation Based on Temporal-Aware Self-Supervised Learning}, US Patent (pending)
    \pubitem \mikelin, Y. Xie, H. Tang, C. Huang, L. Han, W. Fan, \textbf{3D Hand Pose Estimation Based on Depth-image Guided Adversarial Networks}, US Patent (pending)
    \pubitem C. Huang, Z. Qian, H. Tang, Y. Xie, \mikelin, K. Wang, X. Chen, Z. Huo, W. Fan, \textbf{A Deep Learning System for Detecting Acute Intracranial Hemorrhage in Non-Contrast Head CT Images}, US Patent (pending)
    \pubitem C. Huang, Z. Qian, H. Tang, Y. Xie, \mikelin, K. Wang, X. Chen, L. Han, Z. Huo, W. Fan, \textbf{A 2.5-dimensional Convolutional Neural Network for Predicting Hematoma Expansion in Non-Contrast Head CT Images}, US Patent (pending)
    \pubitem H. Tang, Y. Xie, \mikelin, L. Han, W. Fan, \textbf{System and Method for Automatic Recognition for Hand Activity defined in Unified Parkinson Disease Rating Scale}, US Patent (pending)
    \pubitem \mikelin, Y. Xie, H. Tang, L. Han, W. Fan, \textbf{Realistic Hand Pose Synthesis Based on Blending Generative Adversarial Networks (BlendGAN)}, US Patent (pending)
    \pubitem L. Han, H. Tang, Y. Xie, \mikelin, Q. Zhen, Z. Huo, W. Fan, \textbf{PDD: Parkinson Disease Detection Mobile App},  US Patent (pending)
    \pubitem N. Du, K. Wang, M. Tu, S. Zhang, H. Tang, \mikelin, W. Fan, \textbf{A Multimodal Framework for Heart Abnormalities Analysis based on EMR/EHR and Electrocardiography}, US Patent (pending)
    \pubitem L. Han, N. Du, K. Wang, M. Tu, S. Zhang, H. Tang, \mikelin, W. Fan, \textbf{AABB: AI Aided Bug Bits and Transmitted Disease Dentification}, US Patent (pending), US Patent (pending)
    \pubitem Y. Xie, T. Yang, M. Tu, N. Du, \mikelin, W. Fan, \textbf{A Method for Determining Disease Symptom Relations Using Acceptance and Rejection of Random Samples}, US Patent (pending)
    \pubitem \mikelin, Y. Xie, K. Wang, L. Han, W. Fan, \textbf{Augmenting Reliable Training Data with CycleGAN for Hand Pose Estimation}, US Patent (pending)
    \pubitem Y.-P. Hung, \mikelin, \textbf{Re-anchorable Virtual Panel in Three-dimensional Space}, US Patent, US- 20160187991-A1, filed July 23, 2015, and issued October 3, 2016~\href{https://patents.google.com/patent/US9529446}{\faFileTextO}
    \pubitem Y.-P. Hung, \mikelin, \textbf{A Re-anchorable Virtual Panel in 3D Space}, Taiwan Patent, I521387, filed December 25, 2014, and issued February 11, 2016
\PubItemEnd

% ----------- Patents -------------- %
\textbf{Poster:} \vspace{-3pt}
\PubItemStart
    \pubitem S.-C. Chen, C.-W. Hsu, \mikelin, Kevin Lin, Y.-P. Hung, \textbf{Teleport Space: Space Navigation by Detecting the Self-Motion of a Mobile Device}, ACM SIGGRAPH Asia, 2013.
\PubItemEnd